---
title: ''
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## NARRATIVE

By all accounts, Riddler Nation had a lot of fun hunting for the mysterious numbers a few weeks back. So here’s what we’re going to do: For the next four weeks, the Riddler Express will feature a similar puzzle that combines multiplication and logic. We’ll be calling these CrossProducts.

For your first weekly CrossProduct, there are five three-digit numbers — each belongs in a row of the table below, with one digit per cell. The products of the three digits of each number are shown in the rightmost column. Meanwhile, the products of the digits in the hundreds, tens and ones places, respectively, are shown in the bottom row.

`______| _____| ___|  135`
`______| _____| ___|  45`
`______| _____| ___|  64`
`______| _____| ___| 280`
`______| _____| ___|  70`
` 3,000| 3,969|	640|`


Can you find all five three-digit numbers and complete the table?

## SOLUTION


```{r}
row_products <- c(135, 45, 64, 280, 70)

col_products <- c(3000, 3969, 640)

pos_rows <- 
  crossing(a = 1:9, 
           b = 1:9, 
           c = 1:9) %>% 
  mutate(p = a * b * c) %>% 
  filter(p %in% row_products) %>% 
  split(.$p)

for (a in 1:nrow(pos_rows$`45`)) {
  for (b in 1:nrow(pos_rows$`64`)) {
    for (c in 1:nrow(pos_rows$`70`)) {
      for (d in 1:nrow(pos_rows$`135`)) {
        for (e in 1:nrow(pos_rows$`280`)) {
          
          mult <- 
            bind_rows(
              pos_rows$`45`[a, ],
              pos_rows$`64`[b, ],
              pos_rows$`70`[c, ],
              pos_rows$`135`[d, ],
              pos_rows$`280`[e, ]) 
          
          test_col <- 
            mult %>% 
            select(-p) %>% 
            summarize(across(.fns = prod)) %>%
            as.matrix() %>% 
            as.vector() %>% 
            identical(., col_products)
          
          if (test_col) {
            
            answer <- mult
            break
            
          }
          
        }
      }
    }
  }
}

# re-order answer to match input
answer <- 
  answer[match(row_products, answer$p), ]

# rebuild the table to match the prompt
#   for visual verification
bind_rows(
  answer, 
  summarize(select(answer, -p), across(.fns = prod))
)

# write to clipboard for riddler answer form
mutate(answer, p = str_c(a, b, c)) %>% 
  pull(p) %>% 
  str_c(collapse = ", ") #%>% writeClipboard()



```

